Balsa: A Compact Line Notation Based on SMILES

### 2023-01-04 manuscript.tex
Adds ethane valence calculation. Closes #56
Fixes typo. Closes #58

@@

Transformation of graph to tree can be aided by a \textit{pool} (Tabe~\ref{table:pool}). A pool issues a bridge index given an unordered pairing of atomic identifiers. The bridge index will not be re-issued until the pool receives the same pairing again. A pool is used during a depth-first traversal of a molecular graph, where the presence of a cycle is indicated by the discovery of an index that has already been traversed. On encountering a cycle, a bridge index is requested from the pool by submitting the source and target atomic indexes as an unordered pair. The bridge index is then used to construct the first half of the gap bond. Later, the same bond will be traversed in the opposite direction. When it is, a gap index is requested from the pool by re-submitting a source and target index pairing. Doing so yields the bridge index, while simultaneously freeing it for later use.

>>>>

The valence calculation excludes implicit hydrogens. For example, ethane can be encoded such that each carbon has three implicit hydrogens. Although these hydrogens are understood to be bonded, the valence calculation for carbon returns just one.

@@

Transformation of graph to tree can be aided by a \textit{pool} (Table~\ref{table:pool}). A pool issues a bridge index given an unordered pairing of atomic identifiers. The bridge index will not be re-issued until the pool receives the same pairing again. A pool is used during a depth-first traversal of a molecular graph, where the presence of a cycle is indicated by the discovery of an index that has already been traversed. On encountering a cycle, a bridge index is requested from the pool by submitting the source and target atomic indexes as an unordered pair. The bridge index is then used to construct the first half of the gap bond. Later, the same bond will be traversed in the opposite direction. When it is, a gap index is requested from the pool by re-submitting a source and target index pairing. Doing so yields the bridge index, while simultaneously freeing it for later use.
